Constant-round Blind Classical Verification of Quantum Sampling

### 2020-09-04 preliminaries.tex
Add the other aaronson's paper on SampBQP
Talk about SampBQP inverse poly error

We define the sampling version of $\BQP$ based on \cite{aaronson_2013}.

@@

\Ethan{see Scott's paper to see why inverse poly there. Maybe it's just because it's required for his result to work.
More generally, need discussions on sampling vs non sampling
Try to claim our definitions is WLOG/general/intuitive
}
This version has an inverse-polynomial error because...
\Ethan{TODO cite the other paper and something about near-term quantum computers}

>>>>

We define the sampling version of $\BQP$ based on \cite{aaronson_2013, aaronson_arkhipov_2011}.
The definition of $\SampBQP$ allows inverse-polynomial error in order to capture some characteristics of optics-based quantum computing implementations.

@@
